---
title: "UV Index"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(httr)
library(jsonlite)
library(ggplot2)
library(tidyr)
library(dplyr)
library(lubridate)
library(grid)
library(png)
```

```{r echo=FALSE}
env_apikey = Sys.getenv("APIKEY")
```

```{r}
convert_timestamp = function(timestamp) {
  return( as.POSIXct( timestamp ,tz = "Europe/Copenhagen",origin="1970-01-01") )
}
```

```{r}
convert_dataframe_timestamps = function(df) {
  df$dt = convert_timestamp(df$dt)
  df$sunrise = convert_timestamp(df$sunrise)
  df$sunset = convert_timestamp(df$sunset)
  df$moonrise = convert_timestamp(df$moonrise)
  df$moonset = convert_timestamp(df$moonset)
  return( df )
}
```

```{r}
wind_angle_to_compass = function(angle)  {
    val = (angle + 11.25)/22.5
    arr = c("N", "NNE", "NE", "ENE", "E", "ESE", "SE", "SSE", "S", "SSW", "SW", "WSW", "W", "WNW", "NW", "NNW")
    return( arr[(val %% 16)] )
}
```

```{r}
convert_kelvin= function(kelvin) {
  return( kelvin - 273.15 )
}
```


```{r include=TRUE}

lat = 56.1572
lon = 10.2107

res = GET(paste0("https://api.openweathermap.org/data/2.5/onecall?lat=",lat,"&lon=",lon,"&appid=",env_apikey)) # Yeah, should really hide that api key.

res_json = jsonlite::fromJSON( rawToChar( res$content ) )

res_json_current = res_json$current
res_json_daily = res_json$daily
res_json_hourly = res_json$hourly
res_json_minutely = res_json$minutely

res_json_daily = convert_dataframe_timestamps(res_json_daily)
res_json_current = convert_dataframe_timestamps(res_json_current)
res_json_hourly$dt = convert_timestamp(res_json_hourly$dt)
res_json_minutely$dt = convert_timestamp(res_json_minutely$dt)

res_json_current$temp = convert_kelvin( res_json_current$temp )
res_json_current$feels_like = convert_kelvin( res_json_current$feels_like )
res_json_current$dew_point = convert_kelvin( res_json_current$dew_point )

res_json_hourly$temp = convert_kelvin( res_json_hourly$temp )
res_json_hourly$feels_like = convert_kelvin( res_json_hourly$feels_like )
res_json_hourly$dew_point = convert_kelvin( res_json_hourly$dew_point )
```

# Openweather: Current Weather

So you don't need to look out the window. :-)

* Time: ```r res_json_current$dt ```
* Weather Description: ```r res_json_current$weather$description ```
* Temperature (C): ```r res_json_current$temp ```
* Feels Like (C): ```r res_json_current$feels_like ```
* Pressure (hPa): ```r res_json_current$pressure ```
* Humidity: ```r res_json_current$humidity ```
* Dew Point: ```r res_json_current$dew_point ```
* UVI Index: ```r res_json_current$uvi ```
* Clouds: ```r res_json_current$clouds ```
* Visibility: ```r res_json_current$visibility ```
* Wind Speed: ```r res_json_current$wind_speed ```
* Wind Degree: ```r res_json_current$wind_deg ```
* Wind Direction: ```r wind_angle_to_compass( res_json_current$wind_deg )```

# Openweather: Today Outdoors Weather

```{r}

rescale_capped = function(values,from) {
  
  if (from[2]>from[1]) {
    values = pmin(from[2],values)
    values = pmax(from[1],values)
    return( (values-from[1])/(from[2] - from[1]) * 100 )
  } else {
    values = pmin(from[1],values)
    values = pmax(from[2],values)
    #values = from[1] - values
    return( (values-from[1])/(from[2] - from[1]) * 100 )
    
  }
}

```

```{r}

df.scores = res_json_hourly %>% 
  filter(dt<=ymd_hms(paste0(Sys.Date()," 00:00:00"),tz = "Europe/Copenhagen")+days(1)) %>% 
  dplyr::mutate(dt=format(dt,"%H:%M"),
                pop=pop*100) 
# %>% 
  # dplyr::mutate(rain=.$rain$`1h`)

# df.scores$rain[is.na(df.scores$rain)] <- 0

df.scores = df.scores %>% 
  # dplyr::mutate(rain_score=rescale_capped(rain,from = c(10,0))) %>% 
  dplyr::mutate(temp_score=rescale_capped(temp,from = c(0,25))) %>% 
  dplyr::mutate(feels_like_score=rescale_capped(feels_like,from = c(0,25))) %>% 
  dplyr::mutate(humidity_score=rescale_capped(humidity,from = c(100,0))) %>% 
  dplyr::mutate(uvi_score=rescale_capped(uvi,from = c(0,6))) %>% 
  dplyr::mutate(clouds_score=rescale_capped(clouds,from = c(100,0))) %>% 
  dplyr::mutate(wind_speed_score=rescale_capped(wind_speed,from = c(10,0))) %>% 
  dplyr::mutate(wind_gust_score=rescale_capped(wind_gust,from = c(10,0))) %>% 
  dplyr::mutate(pop_score=rescale_capped(pop,from = c(100,0))) 


```

```{r}

draw_scorecard = function(factors) {
  
## First get DT and score

df.score = df.scores %>% 
  dplyr::select(dt,contains(factors),contains(paste0(factors,"_score")))

num_cols = sum(grepl("_score",colnames(df.score)))

df.score = df.score %>% 
  dplyr::mutate(score = round(100*rowSums(across(contains("_score")))/(num_cols*100))) %>% 
  dplyr::select(dt,score,contains(factors),-contains("_score"))

df.dt_score = df.score %>% 
  dplyr::select(dt,score)


# Then gather and join on score
df.score %>% 
  dplyr::select(dt,score,contains(factors)) %>% 
  gather(metric,value,score:ncol(.)) %>% 
  inner_join(df.dt_score, by = "dt") %>% 
  dplyr::mutate(metric=factor(metric,levels=c("score",factors))) %>% 
  ggplot(.,aes(x=metric,y=dt)) +
  geom_tile(aes(fill=score)) + 
  scale_fill_gradient2(low="red",mid="white",high="green",midpoint=50,limits = c(0,100)) +
  geom_text(aes(label=paste0(round(value,0))),color="black") +
  theme_bw() +
  theme(legend.position="null") +
  labs(x=NULL,y=NULL) + 
  scale_x_discrete(labels=c("score" = "Score 0-100",
                            "temp" = "Temperature (C)",
                            "uvi" = "UV Index",
                            "clouds" = "Clouds (%)",
                            "pop" = "Precipitation (%)",
                            "rain" = "Rain (mm)",
                            "wind_speed" = "Wind Speed (m/s)",
                            "wind_gust" = "Wind Gusts (m/s)"))

}

```

## Outdoor Gym

```{r}

order = c("temp","uvi","clouds","pop")
draw_scorecard(order)

```

## Outdoor Sun Not Covered

```{r}

order = c("temp","uvi","clouds","pop")
draw_scorecard(order)

```

## Outdoor Sun Covered

```{r}

order = c("temp","uvi","clouds")
draw_scorecard(order)

```

## Outdoor BBQ Not Covered

```{r}

order = c("temp","pop","clouds","wind_speed","wind_gust")
draw_scorecard(order)

```

# Openweather: Next Days' Outdoors Weather

```{r}

## First get DT and score

df.scores = res_json_hourly %>% 
  filter(!hour(dt) %in% c(23,seq(0,6) )) %>% 
  dplyr::mutate(dt=format(dt,"%A %H:%M"),
                pop=pop*100)
# %>% 
  # dplyr::mutate(rain=.$rain$`1h`)

# df.scores$rain[is.na(df.scores$rain)] <- 0

df.scores = df.scores %>% 
  # dplyr::mutate(rain_score=rescale_capped(rain,from = c(10,0))) %>% 
  dplyr::mutate(temp_score=rescale_capped(temp,from = c(0,25))) %>% 
  dplyr::mutate(feels_like_score=rescale_capped(feels_like,from = c(0,25))) %>% 
  dplyr::mutate(humidity_score=rescale_capped(humidity,from = c(100,0))) %>% 
  dplyr::mutate(uvi_score=rescale_capped(uvi,from = c(0,6))) %>% 
  dplyr::mutate(clouds_score=rescale_capped(clouds,from = c(100,0))) %>% 
  dplyr::mutate(wind_speed_score=rescale_capped(wind_speed,from = c(10,0))) %>% 
  dplyr::mutate(wind_gust_score=rescale_capped(wind_gust,from = c(10,0))) %>% 
  dplyr::mutate(pop_score=rescale_capped(pop,from = c(100,0))) 



```

## Outdoor Gym Not Covered

```{r fig.height = 6, fig.width =7 }

factors = c("temp","uvi","clouds","wind_gust","pop")
draw_scorecard(factors)

```

## Outdoor Sun Not Covered

```{r fig.height = 6, fig.width = 5}

factors = c("temp","uvi","clouds","pop")
draw_scorecard(factors)

```
## Outdoor Sun Covered

```{r fig.height = 6, fig.width = 5}

factors = c("temp","uvi","clouds")
draw_scorecard(factors)

```

## Outdoor BBQ Not Covered

```{r fig.height = 6, fig.width = 7}

factors = c("temp","pop","wind_gust","wind_speed")
draw_scorecard(factors)

```

## Outdoor BBQ Covered

```{r fig.height = 6, fig.width = 7}

factors = c("temp","wind_gust","wind_speed")
draw_scorecard(factors)

```

# Sport X Tan og Træn Index

## Today

```{r fig.width=10,fig.height=5}
library(png)
library(grid)
list.files()

img <- readPNG("assets/SportX_logoorig.png")
g <- rasterGrob(img, interpolate=TRUE)

df.scores_sportx =  res_json_hourly %>% 
  filter(as.Date(dt,tz="Europe/Copenhagen") == Sys.Date()) %>% 
  filter(hour(dt)<=20) %>% 
  dplyr::mutate(dt_label=format(dt,"%H:%M"),
                pop=pop*100)
# %>% 
  # dplyr::mutate(rain=.$rain$`1h`)

# df.scores_sportx$rain[is.na(df.scores_sportx$rain)] <- 0

df.scores_sportx = df.scores_sportx %>% 
  # dplyr::mutate(rain_score=rescale_capped(rain,from = c(10,0))) %>% 
  dplyr::mutate(temp_score=rescale_capped(temp,from = c(0,25))) %>% 
  dplyr::mutate(feels_like_score=rescale_capped(feels_like,from = c(0,25))) %>% 
  dplyr::mutate(humidity_score=rescale_capped(humidity,from = c(100,0))) %>% 
  dplyr::mutate(uvi_score=rescale_capped(uvi,from = c(0,6))) %>% 
  dplyr::mutate(clouds_score=rescale_capped(clouds,from = c(100,0))) %>% 
  dplyr::mutate(wind_speed_score=rescale_capped(wind_speed,from = c(10,0))) %>% 
  dplyr::mutate(wind_gust_score=rescale_capped(wind_gust,from = c(10,0))) %>% 
  dplyr::mutate(pop_score=rescale_capped(pop,from = c(100,0))) 

factors = c("temp","uvi","wind_speed","pop","clouds")

df.score = df.scores_sportx %>% 
  dplyr::select(dt,dt_label,contains(factors),contains(paste0(factors,"_score")))

num_cols = sum(grepl("_score",colnames(df.score)))

df.score = df.score %>% 
  dplyr::mutate(score = round(100*rowSums(across(contains("_score")))/(num_cols*100))) %>% 
  dplyr::select(dt,dt_label,score,contains(factors),-contains("_score"))

df.dt_score = df.score %>% 
  dplyr::select(dt,score)

df.dt_label = df.score %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"\n",round(temp,0),"°C\n")) %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"UV: ",round(uvi,0),"\n")) %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"",round(wind_speed,0),"m\\s\n")) %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"Regn: ",pop,"%\n")) %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"Sky: ",clouds,"%\n")) %>% 
  dplyr::select(dt,dt_label)


dt_label_vector = df.score %>% 
  dplyr::select(dt,score) %>% 
  inner_join(df.dt_label, by = "dt") %>% 
  .[['dt_label']]

index_start = dt_label_vector[1]
index_stop = dt_label_vector[3]

# Then gather and join on score
df.score %>% 
  dplyr::select(dt,score) %>% 
  inner_join(df.dt_label, by = "dt") %>% 
  ggplot(.,aes(x=dt_label,y=score, group=1)) +
  geom_line(color="white") + 
  geom_point(color="white") + 
  geom_text(aes(label=paste0(round(score,0)),vjust=-1),color="white") +
  theme_bw() +
  theme(panel.background = element_rect(fill=rgb(52/255,60/255,72/255)),
        panel.border = element_blank(),
        panel.grid.major = element_line(color=rgb(235, 235, 235, 100, maxColorValue = 255)),
        panel.grid.minor = element_blank(),
        axis.text.x= element_text(colour = "white"),
        panel.grid.major.x = element_blank(),
        axis.text.y= element_text(colour = "white"),
        axis.title.y= element_text(colour = "white",size=20),
        axis.line = element_line(colour = "white"),
        plot.background = element_rect(fill = rgb(52/255,60/255,72/255))) +
  scale_y_continuous(limits=c(0,100),expand=c(0,0),breaks=seq(0,100,by=20)) +
  # scale_x_discrete(breaks=NULL) +
  labs(x=NULL,y="Sport X - Tan & Træn Index! (0-100)")  +
  annotation_custom(g, xmin=index_start, xmax=index_stop, ymin=80, ymax=100)
# +
  # annotate(geom="text", label="- Tan og Træn Index!", x=index_stop, y=7.5, color="white",size=20)


```


## Tomorrow

```{r fig.width=10,fig.height=5}


df.scores_sportx =  res_json_hourly %>% 
  filter(as.Date(dt,tz="Europe/Copenhagen") == Sys.Date()+days(1)) %>% 
  filter(hour(dt)>=10) %>% 
  filter(hour(dt)<=20) %>% 
  dplyr::mutate(dt_label=format(dt,"%H:%M"),
                pop=pop*100) 
# %>% 
  # dplyr::mutate(rain=.$rain$`1h`)

# df.scores_sportx$rain[is.na(df.scores_sportx$rain)] <- 0

df.scores_sportx = df.scores_sportx %>% 
  # dplyr::mutate(rain_score=rescale_capped(rain,from = c(10,0))) %>% 
  dplyr::mutate(temp_score=rescale_capped(temp,from = c(0,25))) %>% 
  dplyr::mutate(feels_like_score=rescale_capped(feels_like,from = c(0,25))) %>% 
  dplyr::mutate(humidity_score=rescale_capped(humidity,from = c(100,0))) %>% 
  dplyr::mutate(uvi_score=rescale_capped(uvi,from = c(0,6))) %>% 
  dplyr::mutate(clouds_score=rescale_capped(clouds,from = c(100,0))) %>% 
  dplyr::mutate(wind_speed_score=rescale_capped(wind_speed,from = c(10,0))) %>% 
  dplyr::mutate(wind_gust_score=rescale_capped(wind_gust,from = c(10,0))) %>% 
  dplyr::mutate(pop_score=rescale_capped(pop,from = c(100,0))) 

factors = c("temp","uvi","wind_speed","pop","clouds")

df.score = df.scores_sportx %>% 
  dplyr::select(dt,dt_label,contains(factors),contains(paste0(factors,"_score")))

num_cols = sum(grepl("_score",colnames(df.score)))

df.score = df.score %>% 
  dplyr::mutate(score = round(100*rowSums(across(contains("_score")))/(num_cols*100))) %>% 
  dplyr::select(dt,dt_label,score,contains(factors),-contains("_score"))

df.dt_score = df.score %>% 
  dplyr::select(dt,score)

df.dt_label = df.score %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"\n",round(temp,0),"°C\n")) %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"UV: ",round(uvi,0),"\n")) %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"",round(wind_speed,0),"m/s\n")) %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"Regn: ",pop,"%\n")) %>% 
  dplyr::mutate(dt_label=paste0(dt_label,"Sky: ",clouds,"%\n")) %>% 
  dplyr::select(dt,dt_label)


dt_label_vector = df.score %>% 
  dplyr::select(dt,score) %>% 
  inner_join(df.dt_label, by = "dt") %>% 
  .[['dt_label']]

# Then gather and join on score
df.score %>% 
  dplyr::select(dt,score) %>% 
  inner_join(df.dt_label, by = "dt") %>% 
  ggplot(.,aes(x=dt_label,y=score, group=1)) +
  geom_line(color="white") + 
  geom_point(color="white") + 
  geom_text(aes(label=paste0(round(score,0)),vjust=-1),color="white") +
  theme_bw() +
  theme(panel.background = element_rect(fill=rgb(52/255,60/255,72/255)),
        panel.border = element_blank(),
        panel.grid.major = element_line(color=rgb(235, 235, 235, 100, maxColorValue = 255)),
        panel.grid.minor = element_blank(),
        axis.text.x= element_text(colour = "white"),
        plot.title = element_text(colour = "white",size=50),
        axis.title.y= element_text(colour = "white",size=20),
        panel.grid.major.x = element_blank(),
        axis.text.y= element_text(colour = "white"),
        axis.line = element_line(colour = "white"),
        plot.background = element_rect(fill = rgb(52/255,60/255,72/255))) +
  scale_y_continuous(limits=c(0,100),expand=c(0,0)) +
  labs(x=NULL,y="Sport X - Tan & Træn Index! (0-100)")  +
  annotation_custom(g, xmin=index_start, xmax=index_stop, ymin=80, ymax=100)


```


# Openweather: Minutely Forecast

## Precipitation


```{r}

ggplot(res_json_minutely,aes(x=dt,y=precipitation)) +
  geom_line(color="red",size=2) +
  scale_y_continuous(expand=c(0,0),limits=c(0,15)) +
  scale_x_datetime(date_breaks = "5 mins",date_labels = "%H:%M") +
  geom_vline(xintercept = Sys.time()) +
  theme_bw() +
  labs(y="Estimated precipitation (mm)",x="Time")

```

# Openweather: Hourly Forecast

```{r echo=FALSE}

hourly_x_datetime = scale_x_datetime(date_labels = "%A %H:%M",date_breaks = "4 hour")
theme_hourly = theme_bw() + theme(axis.text.x = element_text(angle=45,hjust=1))

date_seq = ymd_hms(paste0(seq.Date(as.Date(min(res_json_hourly$dt)),as.Date(max(res_json_hourly$dt)),by = "1 day")," 00:00:00"),tz = "Europe/Copenhagen")
date_seq_midday = ymd_hms(paste0(seq.Date(as.Date(min(res_json_hourly$dt)),as.Date(max(res_json_hourly$dt)),by = "1 day")," 12:00:00"),tz = "Europe/Copenhagen")

vlines_midnight = geom_vline(xintercept = date_seq,color="gray20")
vlines_midday = geom_vline(xintercept = date_seq_midday,color="red")

```

## Temperature

```{r}

ggplot(res_json_hourly,aes(x=dt,y=temp)) +
  geom_line() +
  scale_y_continuous(expand=c(0,0),limits=c(-5,30),breaks = seq(-5,30,by=2.5)) +
  hourly_x_datetime +
  theme_hourly +
  vlines_midnight + 
  vlines_midday +
  labs(y="Estimated Temperature (C)",x="Time",title="Temperature (C)") +
  annotate("rect",ymin = -5,ymax = 0,fill="blue",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 0,ymax = 5,fill="lightsteelblue",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 5,ymax = 10,fill="green",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 10,ymax = 15,fill="yellow",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 15,ymax = 20,fill="orange",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 20,ymax = 30,fill="red",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3)

```

## Pressure

```{r}

ggplot(res_json_hourly,aes(x=dt,y=pressure)) +
  geom_hline(yintercept = 1013,color="black") +
  geom_line() +
  hourly_x_datetime +
  vlines_midnight + 
  vlines_midday +
  scale_y_continuous(expand=c(0,0),limits=c(1013-40,1013+40)) +
  theme_hourly +
  labs(y="Estimated Pressure (hPa)",x="Time",title="Pressure")

```

## Humidity

```{r}

ggplot(res_json_hourly,aes(x=dt,y=humidity)) +
  geom_line() +
  scale_y_continuous(expand=c(0,0),limits=c(0,NA)) +
  hourly_x_datetime +
  vlines_midnight + 
  vlines_midday +
  theme_hourly +
  labs(y="Estimated Humidity (%)",x="Time",title="Humidity (%)") +
  annotate("rect",ymin = 0,ymax = 30,fill="blue",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 30,ymax = 60,fill="green",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 60,ymax = 100,fill="orange",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) 

```

## UVI Index

```{r}

ggplot(res_json_hourly,aes(x=dt,y=uvi)) +
  geom_line() +
  scale_y_continuous(expand=c(0,0),limits=c(0,NA),breaks = seq(0,11,by=1),labels = scales::number_format(accuracy = 1)) +
  hourly_x_datetime +
  vlines_midnight + 
  vlines_midday +
  theme_hourly +
  labs(y="Estimated UV Index ()",x="Time",title="UV Index") +
  annotate("rect",ymin = 0,ymax = 2,fill="green",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 2,ymax = 6,fill="yellow",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 6,ymax = 8,fill="orange",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 8,ymax = 10,fill="red",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  geom_vline(xintercept = Sys.time()) 

```

## Cloud Coverage

```{r}

ggplot(res_json_hourly,aes(x=dt,y=clouds)) +
  geom_line() +
  scale_y_continuous(expand=c(0,0),limits=c(0,NA)) +
  vlines_midnight + 
  vlines_midday +
  hourly_x_datetime +
  theme_hourly +
  labs(y="Estimated Clouds (C)",x="Time",title="Clouds (C)") +
  annotate("rect",ymin = 0,ymax = 100/3,fill="green",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 1*100/3,ymax = 2*100/3,fill="yellow",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 2*100/3,ymax = 100,fill="orange",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  scale_x_datetime(date_labels = "%A") +
  geom_vline(xintercept = Sys.time()) 

```

## Wind Speed

```{r}

ggplot(res_json_hourly,aes(x=dt,y=wind_speed)) +
  geom_line() +
  scale_y_continuous(expand=c(0,0),limits=c(0,NA)) +
  hourly_x_datetime +
  vlines_midnight + 
  vlines_midday +
  geom_vline(xintercept = Sys.time()) + 
  theme_hourly +
  labs(y="Wind Speed",x="Time",title="Wind Speed (Avg & Gust)") +
  geom_line(data=res_json_hourly,aes(x=dt,y=wind_gust),color="red") +
  annotate("rect",ymin = 0,ymax = 4,fill="green",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 4,ymax = 10,fill="yellow",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 10,ymax = 20,fill="orange",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3)

```


## Wind Degree

```{r}

ggplot(res_json_hourly,aes(x=dt,y=wind_deg)) +
  geom_line() +
  vlines_midnight + 
  vlines_midday +
  scale_y_continuous(expand=c(0,0),limits=c(0,NA)) +
  hourly_x_datetime +
  geom_vline(xintercept = Sys.time()) + 
  theme_hourly +
  labs(y="Wind Degree",x="Time",title="Wind Degree")

```

##  Probability of Precipitation

```{r}

ggplot(res_json_hourly,aes(x=dt,y=pop)) +
  geom_line() +
  vlines_midnight + 
  vlines_midday +
  scale_y_continuous(expand=c(0,0),limits=c(0,1),labels=scales::percent) +
  hourly_x_datetime +
  theme_hourly +
  geom_vline(xintercept = Sys.time()) + 
  labs(y="Probability of Precipitation",x="Time",title="Probability of Precipitation") +
  annotate("rect",ymin = 0,ymax = 0.25,fill="green",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 0.25,ymax = 0.75,fill="yellow",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3) +
  annotate("rect",ymin = 0.75,ymax = 1,fill="orange",xmin = min(res_json_hourly$dt),xmax = max(res_json_hourly$dt),alpha=0.3)

```


# Openweather: Daily Forecast


```{r echo=FALSE}

daily_x_datetime = scale_x_datetime(date_labels = "%A %b %d",date_breaks = "1 day")
theme_daily = theme_bw() + theme(axis.text.x = element_text(angle=45,hjust=1))

date_seq = ymd_hms(paste0(seq.Date(as.Date(min(res_json_daily$dt)),as.Date(max(res_json_daily$dt)),by = "1 day")," 00:00:00"),tz = "Europe/Copenhagen")
date_seq_midday = ymd_hms(paste0(seq.Date(as.Date(min(res_json_daily$dt)),as.Date(max(res_json_daily$dt)),by = "1 day")," 12:00:00"),tz = "Europe/Copenhagen")

vlines_midnight = geom_vline(xintercept = date_seq,color="gray60")
vlines_midday = geom_vline(xintercept = date_seq_midday,color="red",alpha=0.3)

```

## UV Index

```{r}

ggplot(res_json_daily,aes(x=dt,y=uvi)) +
  geom_line() +
  scale_y_continuous(expand=c(0,0),limits=c(0,11),labels = scales::number_format(accuracy = 1),breaks = seq(0,11,by=1)) +
  annotate("rect",ymin = 0,ymax = 2,fill="green",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 2,ymax = 6,fill="yellow",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 6,ymax = 8,fill="orange",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 8,ymax = 11,fill="red",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  daily_x_datetime +
  theme_daily +
  vlines_midnight + 
  vlines_midday + 
  geom_vline(xintercept = Sys.time()) + 
  labs(y="UV Index",x="Time",title="UV Index")

```



```{r eval=F}
## Rain
ggplot(res_json_daily,aes(x=dt,y=rain)) +
  geom_line() +
  geom_vline(xintercept = Sys.time()) + 
  scale_y_continuous(expand=c(0,0),limits=c(0,NA)) +
  daily_x_datetime +
  theme_daily +
  vlines_midnight + 
  vlines_midday + 
  labs(y="Rain (mm)",x="Time",title="Rain (mm)")

```

## Probability of Precipitation

```{r}

ggplot(res_json_daily,aes(x=dt,y=pop)) +
  geom_line() +
  geom_vline(xintercept = Sys.time()) + 
  scale_y_continuous(expand=c(0,0),limits=c(0,NA), labels = scales::percent) +
  daily_x_datetime +
  theme_daily +
  vlines_midnight + 
  vlines_midday + 
  labs(y="Probability of Precipitation",x="Time",title="Probability of Precipitation")+
  annotate("rect",ymin = 0,ymax = 0.25,fill="green",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 0.25,ymax = 0.75,fill="yellow",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 0.75,ymax = 1,fill="orange",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3)

```


## Clouds

```{r}

ggplot(res_json_daily,aes(x=dt,y=clouds)) +
  geom_line() +
  geom_vline(xintercept = Sys.time()) + 
  scale_y_continuous(expand=c(0,0),limits=c(0,NA)) +
  daily_x_datetime +
  theme_daily +
  vlines_midnight + 
  vlines_midday + 
  labs(y="Cloud Coverage",x="Time",title="Cloud Coverage")+
  annotate("rect",ymin = 0,ymax = 100/3,fill="green",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 1*100/3,ymax = 2*100/3,fill="yellow",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 2*100/3,ymax = 100,fill="orange",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) 

```

## Wind Gusts

```{r}

ggplot() +
  geom_line(data = res_json_daily,aes(x=dt,y=wind_speed)) +
  scale_y_continuous(expand=c(0,0),limits=c(0,NA)) +
  daily_x_datetime +
  theme_daily +
  vlines_midnight + 
  vlines_midday + 
  geom_vline(xintercept = Sys.time()) + 
  geom_line(data=res_json_daily,aes(x=dt,y=wind_gust),color="red") +
  labs(y="Wind",x="Time",title="Wind ") +
  annotate("rect",ymin = 0,ymax = 4,fill="green",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 4,ymax = 10,fill="yellow",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 10,ymax = 20,fill="orange",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3)

```

## Temperature

```{r}

res_json_daily %>% 
  dplyr::select(dt) %>% 
  bind_cols(res_json_daily$temp) %>% 
  gather(temp,value,day:morn) %>% 
  dplyr::mutate(value=convert_kelvin(value)) %>% 
  ggplot(.,aes(x=dt,y=value)) +
  geom_vline(xintercept = Sys.time()) + 
  geom_line(aes(color=temp)) +
  scale_y_continuous(limits=c(0,30),expand=c(0,0)) +
  daily_x_datetime +
  theme_daily +
  vlines_midnight + 
  vlines_midday + 
  theme(legend.position = "bottom") +
  labs(x="Date",y="Temperature (C)",title = "Temperature (C)") +
  annotate("rect",ymin = -5,ymax = 0,fill="blue",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 0,ymax = 5,fill="lightsteelblue",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 5,ymax = 10,fill="green",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 10,ymax = 15,fill="yellow",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 15,ymax = 20,fill="orange",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) +
  annotate("rect",ymin = 20,ymax = 30,fill="red",xmin = min(res_json_daily$dt),xmax = max(res_json_daily$dt),alpha=0.3) 

```





